\documentclass[10.5pt,a4paper]{article}

\usepackage[left=0.50in,right=0.50in,top=0.40in,bottom=0.40in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}

\definecolor{headingblue}{RGB}{20,35,95}
\definecolor{subtext}{RGB}{70,70,70}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1.04}

\titleformat{\section}
{\bfseries\large\color{headingblue}}
{}
{0em}
{}
[\vspace{1pt}\titlerule\vspace{-3pt}]

\titlespacing*{\section}{0pt}{9pt}{9pt}

\setlist[itemize]{leftmargin=12pt,itemsep=0.8pt,topsep=1pt,parsep=0pt,partopsep=0pt}
\renewcommand{\arraystretch}{0.92}
\hyphenation{PHPMailer}

\newcommand{\role}[2]{\textbf{#1} \hfill \textit{#2}}

\begin{document}

%================ HEADER ==================
\begin{center}
{\Huge \textbf{PAVAN KUMAR G S}}\\[4pt]
\textcolor{subtext}{Bengaluru, Karnataka \ — \ +91-6360693609 \ — \ ganeshpavan2004@gmail.com}\\[1pt]
\textcolor{subtext}{LinkedIn: \href{https://linkedin.com/in/pavan-kumar-g-s-600804277}{linkedin.com/in/pavan-kumar-g-s-600804277} \ — \ GitHub: \href{https://github.com/pavan-gs-dev}{github.com/pavan-gs-dev}}
\end{center}
\vspace{-10pt}

%================ SUMMARY ==================
\section*{PROFESSIONAL SUMMARY}
Python Full Stack Developer with hands-on experience designing, developing, and deploying \textbf{8+ web and mobile applications} across the full software development life cycle. Proficient in \textbf{Python, FastAPI, Django, Flask, PostgreSQL, MySQL}, and \textbf{REST API} design. Skilled in building scalable backend systems, implementing secure authentication workflows, integrating third-party APIs, and optimizing application performance. Published \textbf{2 Android applications} on the Google Play Store and maintained production-grade applications on Linux VPS environments. Strong foundation in software design patterns, database design, version control with Git, and agile development best practices.

%================ SKILLS ==================
\section*{TECHNICAL SKILLS}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
Languages         & Python, PHP, Dart, JavaScript \\
Backend           & FastAPI, Django, Flask, REST API Design, JWT Authentication, OAuth 2.0, Session Management \\
Frontend          & HTML, CSS, JavaScript, Responsive Web Design, SPA Architecture \\
Databases         & PostgreSQL, MySQL, SQLite, RoomDB, Relational Database Design \\
Mobile            & Flutter, Android Studio, Java \\
DSA               & Arrays, Linked Lists, Trees, Graphs, Hashing, Dynamic Programming, Sorting Algorithms \\
Tools \& Platforms & Git, GitHub, Linux, Ubuntu Server, Apache, Cloudflare, SMTP, Unit Testing \\
\end{tabularx}

%================ PROJECTS ==================
\section*{PROJECT EXPERIENCE}

\role{Production Full-Stack Web Platform}{Python, PHP, MySQL, JavaScript, Apache, Ubuntu}
\begin{itemize}
\item Designed and developed a production-ready \textbf{Single Page Application (SPA)} with a scalable architecture, native app-like navigation, and a responsive, mobile-first interface following software engineering best practices.
\item Implemented a secure \textbf{authentication} system featuring JWT-based session management, auto-login, password reset flows, email verification, and \textbf{SMTP} integration — closely mirroring real-world backend authentication patterns.
\item Developed and maintained a complete admin management backend spanning \textbf{25+ relational database tables} and \textbf{90+ backend components} covering user management, payments, and administrative operations.
\item Deployed, configured, and maintained the application on a \textbf{Linux VPS} with Apache, Cloudflare DNS, SSL security, and server hardening — managing the full deployment lifecycle end to end.
\item Debugged and optimized backend performance, ensuring scalable database queries and reliable system uptime in a live production environment.
\end{itemize}

\role{AI Face Finder — Python Web Application}{Python, Flask, OpenCV, REST API, Face Recognition}
\begin{itemize}
\item Designed and developed a face-recognition web application enabling photographers to upload event photos and attendees to locate their own images via selfie-based matching.
\item Engineered an automated facial-matching pipeline using \textbf{OpenCV} and the \textbf{Face Recognition} library, eliminating manual photo searches and reducing retrieval time significantly.
\item Implemented backend \textbf{REST API} endpoints with Flask for authentication, event management, and photo handling; integrated third-party libraries to extend core functionality.
\item Tested and debugged the end-to-end pipeline to ensure accurate face matching and a smooth user experience across varied input conditions.
\end{itemize}

\role{Android Applications — Google Play Store}{Java, Android Studio, SQLite, RoomDB}
\begin{itemize}
\item Developed, tested, and published \textbf{2 Android applications} on the Google Play Store, delivering multiple production releases and iterative updates based on user feedback.
\item Designed responsive Android interfaces and implemented local data persistence using \textbf{SQLite} and \textbf{RoomDB}, applying software design patterns for maintainable, scalable mobile code.
\end{itemize}

\textbf{Additional Projects:} AI Face Attendance System — Expense Manager REST API (Python/FastAPI) \ — \ Colour Space Business Website (PHP) \ — \ Cross-Platform Study App (Flutter)

%================ ACHIEVEMENTS ==================
\section*{KEY ACHIEVEMENTS}
\begin{itemize}
\item Designed and implemented secure, scalable \textbf{authentication} systems — including email verification, password reset, auto-login, and session management — across multiple production applications.
\item Integrated \textbf{Cloudflare} for DNS management, SSL/TLS security, caching optimization, and application protection in a live deployment environment.
\item Configured \textbf{PHPMailer} with SMTP authentication to automate transactional emails and account-recovery workflows, improving reliability and user experience.
\item Deployed, maintained, and optimized production applications on \textbf{Linux VPS} servers with Apache configuration, server hardening, and ongoing performance monitoring.
\item Designed and optimized \textbf{relational database} schemas across PostgreSQL and MySQL for secure, scalable, and high-performance data management.
\item Applied software design patterns and best practices — including code modularity, separation of concerns, and version control with \textbf{Git} — consistently across all projects.
\end{itemize}

%================ EDUCATION ==================
\section*{EDUCATION}
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{Bachelor of Engineering, Computer Science} & 2022 -- 2026 \\
Ghousia College of Engineering, Bengaluru (VTU Affiliated) & \\
\end{tabularx}

%================ CERTIFICATIONS ==================
\section*{CERTIFICATION}
MindMatrix Internship Program \ — \ Android Application Development using Generative AI

\end{document}