\documentclass[10pt,a4paper]{article}

\usepackage[left=0.37in,right=0.37in,top=0.35in,bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}

\definecolor{headingblue}{RGB}{25,40,110}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}

\titleformat{\section}
{\large\bfseries\color{headingblue}}
{}
{0em}
{}
[\titlerule]

\titlespacing*{\section}{0pt}{3pt}{1pt}

\begin{document}

%================ HEADER ==================

\begin{center}
{\Huge \textbf{PAVAN KUMAR G S}}\\[2pt]

Bengaluru $\cdot$
+91-6360693609 $\cdot$
ganeshpavan2004@gmail.com $\cdot$
\href{https://linkedin.com/in/pavan-kumar-g-s-600804277}{linkedin.com/in/pavan-kumar-g-s-600804277}
$\cdot$
\href{https://github.com/pavan-gs-dev}{github.com/pavan-gs-dev}

\end{center}

%================ SUMMARY ==================

\section*{SUMMARY}

Full Stack Developer with hands-on experience building and deploying \textbf{8+ real-world web, mobile, and AI-powered applications} using \textbf{Python, FastAPI, Django, PHP, Flutter, PostgreSQL, MySQL, JavaScript, and Java}. Developed scalable REST APIs, Single Page Applications (SPA), admin management systems, and secure authentication solutions using \textbf{JWT, OAuth, and session-based authentication}. Successfully published \textbf{2 Android applications on Google Play Store} and deployed a production full-stack website on a VPS server. Built \textbf{3 machine learning projects} using OpenCV, TensorFlow, and Keras. Experienced in leveraging AI-assisted development to accelerate application design, implementation, and problem-solving. Strong foundation in software development, Linux, Git, and modern full-stack architecture.

%================ PROJECTS ==================

\section*{PROJECTS}

\textbf{Android Applications Published on Google Play Store}
\hfill \textit{Java, Android Studio, SQLite, RoomDB}

\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
\item Developed and successfully published \textbf{2 Android applications} on Google Play Store with multiple production releases and updates.
\item Designed responsive Android interfaces and implemented local data persistence using SQLite and RoomDB.
\end{itemize}

\textbf{AI Face Finder}
\hfill \textit{Python, Flask, OpenCV, Face Recognition}

\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
\item Developed a face-recognition web application enabling photographers to upload event photos and users to find their photos via selfie matching.
\item Implemented automated facial matching using OpenCV and Face Recognition, eliminating manual photo searches.
\item Built authentication, dashboard management, event photo management, and web interfaces using Flask, HTML, CSS, and JavaScript.
\end{itemize}

\textbf{Production Full-Stack SPA Platform}
\hfill \textit{PHP, MySQL, JavaScript, Apache, Ubuntu}

\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
\item Developed and deployed a production-ready Single Page Application (SPA) with native app-like navigation and responsive mobile-first design.
\item Implemented secure authentication using sessions, auto-login, password reset, email verification, and PHPMailer SMTP integration.
\item Built a complete admin management system with \textbf{25+ database tables} and \textbf{90+ backend modules}.
\item Managed VPS deployment, Apache configuration, Cloudflare integration, and server hardening.
\end{itemize}

\textbf{AI Study Planner \& Community Platform}
\hfill \textit{Flutter, FastAPI, PostgreSQL}

\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt]
\item Developed a cross-platform study management application with schedules, reminders, and productivity tracking.
\item Built JWT-based authentication and REST APIs using FastAPI and PostgreSQL.
\item Implemented recommendation-based social feed features and AI-assisted learning tools.
\end{itemize}

\textbf{Additional Projects:}
AI Face Attendance System, Expense Manager API, AutismNetX Prediction System, Nalla-Nuddi Android Application, Full-Stack E-Commerce Platform, Colour Space Business Website, Flutter Study Application with Local Storage and Notifications.

%================ SKILLS ==================

\section*{CORE SKILLS}

\textbf{Languages:} Python, PHP, Java, JavaScript, Dart, HTML5, CSS3, XML (Basic)

\textbf{Backend:} FastAPI, Django, Flask, REST APIs, JWT Authentication, Session Authentication, OAuth 2.0

\textbf{Frontend:} Vanilla JavaScript, SPA Architecture, Responsive Web Design

\textbf{Mobile Development:} Flutter, Android Studio

\textbf{Databases:} PostgreSQL, MySQL

\textbf{AI/ML:} OpenCV, TensorFlow, Keras, Face Recognition, Deep Learning

\textbf{DevOps \& Deployment:} Ubuntu Server, Apache, VPS Management, Linux Administration, Git, GitHub

\textbf{Authentication \& Security:} JWT, Session Management, Google OAuth, Auto Login Systems

\textbf{Tools \& Services:} Photoshop, PHPMailer, SMTP2GO, Postman, Git, GitHub, Linux

\textbf{Cloud/Server:} Apache, VPS Deployment

%================ ACHIEVEMENTS ==================

\section*{ACHIEVEMENTS \& IMPACT}

\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=0pt,parsep=0pt]
\item Published \textbf{2 Android applications} on Google Play Store.
\item Built and deployed multiple full-stack web applications.
\item Developed authentication and database systems for production projects.
\item Managed server deployment and maintenance independently.
\item Completed \textbf{8+ software development projects}.
\end{itemize}


%================ EDUCATION ==================

\section*{EDUCATION}

\begin{tabularx}{\textwidth}{Xr}
\textbf{B.Tech, Computer Science}
&
Ghousia College Of Engineering (2022--2026), Ramanagara-562159
\end{tabularx}

%================ CERTIFICATIONS ==================

\section*{CERTIFICATIONS}

MindMatrix Internship Certificate -- Full Stack Development

\end{document}