\documentclass[10pt,a4paper]{article}

\usepackage[left=0.37in,right=0.37in,top=0.35in,bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}

\definecolor{headingblue}{RGB}{25,40,110}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.3pt}
\linespread{1.0}

\titleformat{\section}
{\large\bfseries\color{headingblue}}
{}
{0em}
{}
[\titlerule]

\titlespacing*{\section}{0pt}{3.5pt}{2pt}

\setlist[itemize]{leftmargin=*,itemsep=0.5pt,topsep=0.5pt,parsep=0pt}

\begin{document}

%================ HEADER ==================

\begin{center}
{\Huge \textbf{PAVAN KUMAR G S}}\\[2pt]

Bengaluru $\cdot$
+91-6360693609 $\cdot$
ganeshpavan2004@gmail.com $\cdot$
\href{https://linkedin.com/in/pavan-kumar-g-s-600804277}{linkedin.com/in/pavan-kumar-g-s-600804277}
$\cdot$
\href{https://github.com/pavan-gs-dev}{github.com/pavan-gs-dev}

\end{center}

%================ SUMMARY ==================

\section*{SUMMARY}

Full Stack Developer with hands-on experience building and deploying \textbf{8+ web and mobile applications} using \textbf{Python, PHP, Flutter, FastAPI, Django, PostgreSQL, and MySQL}. Experienced in developing REST APIs, Single Page Applications (SPA), admin dashboards, and secure authentication systems. Published \textbf{2 Android applications on Google Play Store} and deployed production applications on Linux VPS servers. Strong foundation in software development, databases, Git, and modern web technologies.

%================ PROJECTS ==================

\section*{PROJECTS}

\textbf{Android Applications Published on Google Play Store}
\hfill \textit{Java, Android Studio}

\begin{itemize}
\item Developed and successfully published \textbf{2 Android applications} on Google Play Store with multiple production releases and updates.
\item Designed responsive Android interfaces and implemented local data persistence using SQLite and RoomDB.
\end{itemize}

\textbf{AI Face Finder}
\hfill \textit{Python, Flask, OpenCV, Face Recognition}

\begin{itemize}
\item Developed a face-recognition web application enabling photographers to upload event photos and users to find their photos via selfie matching.
\item Implemented automated facial matching using OpenCV and Face Recognition, eliminating manual photo searches.
\item Built authentication, dashboard management, event photo management, and web interfaces using Flask, HTML, CSS, and JavaScript.
\end{itemize}

\textbf{Production Full-Stack SPA Platform}
\hfill \textit{PHP, MySQL, JavaScript, Apache, Ubuntu}

\begin{itemize}
\item Developed and deployed a production-ready Single Page Application (SPA) with native app-like navigation and responsive mobile-first design.
\item Implemented secure authentication using sessions, auto-login, password reset, email verification, and PHPMailer SMTP integration.
\item Built a complete admin management system with \textbf{25+ database tables} and \textbf{90+ PHP components across authentication, user management, payments, and admin operations}.
\item Managed VPS deployment, Apache configuration, Cloudflare integration, and server hardening.
\end{itemize}

\textbf{AI Study Planner \& Community Platform}
\hfill \textit{Flutter, FastAPI, PostgreSQL}

\begin{itemize}
\item Developed a cross-platform study management application with schedules, reminders, and productivity tracking.
\item Built JWT-based authentication and REST APIs using FastAPI and PostgreSQL.
\item Implemented recommendation-based social feed features and AI-assisted learning tools.
\end{itemize}

\textbf{Additional Projects:} Python (AI Face Attendance System, Expense Manager API, AutismNetX Prediction System), PHP (Full-Stack E-Commerce Platform, Colour Space Business Website), Java (Nalla-Nuddi Android Application), Flutter (Study Application with Local Storage).

%================ SKILLS ==================


\section*{CORE SKILLS}

\textbf{Programming:} Python, PHP, Java, JavaScript, Dart

\textbf{Web Development:} HTML5, CSS3, Responsive Web Design, REST APIs

\textbf{Backend:} FastAPI, Django, Flask, JWT Authentication, OAuth 2.0

\textbf{Frontend:} Vanilla JavaScript, SPA Architecture

\textbf{Mobile Development:} Flutter, Android Studio

\textbf{Databases:} PostgreSQL, MySQL

\textbf{Tools:} Git, GitHub, Postman, Linux, Photoshop

\textbf{Deployment:} Ubuntu Server, Apache, VPS Management


%================ ACHIEVEMENTS ==================
\section*{ACHIEVEMENTS \& IMPACT}

\begin{itemize}
\item Implemented secure authentication systems including email verification, password reset, auto-login, and session management.
\item Integrated Cloudflare services for DNS management, SSL security, caching optimization, and application protection.
\item Configured PHPMailer with SMTP authentication for automated transactional emails and account recovery workflows.
\item Deployed and maintained production applications on Linux VPS servers with Apache configuration and server hardening.
\item Designed and optimized robust database systems to support secure, scalable, and high-performance applications.
\end{itemize}

%================ EDUCATION ==================

\section*{EDUCATION}

\begin{tabularx}{\textwidth}{Xr}
\textbf{B.Tech, Computer Science}
&
Ghousia College Of Engineering (2022--2026), Ramanagara-562159
\end{tabularx}

%================ CERTIFICATIONS ==================

\section*{CERTIFICATIONS}

MindMatrix Internship Certificate -- Full Stack Development

\end{document}
